\documentclass[letterpaper,twocolumn]{article}

%% Bubble answer sheet by Steven Segletes,
%% https://tex.stackexchange.com/a/219531

\usepackage{tikz,graphicx}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[colorlinks]{hyperref}
\usepackage[usestackEOL]{stackengine}
%%\usepackage[draft]{flowfram}
%%\usepackage{flowfram}
%%\ffvadjustfalse
%%\setlength{\columnsep}{1cm}
%%\Ncolumn{3}

\frenchspacing

\newcommand{\repeatntimes}[2]{
   \newcount\i
   \i=0
   \newtoks\ans
   \loop
      \ans=\expandafter{\the\ans #2}
      \advance\i by 1
      \ifnum\i<#1\repeat
   \the\ans
}

\newcommand{\countRepeatntimes}[2]{
   \newcount\i
   \i=0
   \newtoks\ans
   \loop
      \advance\i by 1
      \ans=\expandafter{\the\ans #2}
      \ifnum\i<#1\repeat
   \the\ans
}

\newcounter{problem}
\newcounter{choice}
\newcommand{\generateTable}[1]{%
\countRepeatntimes{#1}{\stepcounter{problem}\makebox[2ex][r]{\theproblem.}%\indent
\setcounter{choice}{0}%
\repeatntimes{4}{\stepcounter{choice}\textcolor{black!35}{%
  \raisebox{0.5pt}{\scalebox{1.0}{\stackinset{c}{}{c}{}{%
    \scalebox{.6}{\footnotesize \Alph{choice}}}{$\bigcirc$}}}} }\par
    \smallskip
}
}

\def\sampleblock{%
  \makebox[5.1ex]{}
  \stepcounter{choice}\textcolor{black!35}{%
   \raisebox{-1.5pt}{\scalebox{1.0}{\stackinset{c}{}{c}{}{%
    \scalebox{.6}{\footnotesize \Alph{choice}}}{$\bigcirc$}}}}
  \stepcounter{choice}\textcolor{black!35}{%
   \raisebox{-1.5pt}{\scalebox{1.0}{\stackinset{c}{}{c}{}{%
    \scalebox{.6}{\footnotesize \Alph{choice}}}{$\bigcirc$}}}}
  \stepcounter{choice}\textcolor{black!35}{%
   \smash{\raisebox{-1.5pt}{\scalebox{1.0}{\stackinset{c}{}{c}{-2.5pt}{%
    \scalebox{8}{\color{black}$\cdot$}}{$\bigcirc$}}}}}
  \stepcounter{choice}\textcolor{black!35}{%
   \raisebox{-1.5pt}{\scalebox{1.0}{\stackinset{c}{}{c}{}{%
    \scalebox{.6}{\footnotesize \Alph{choice}}}{$\bigcirc$}}}}
\par}
\voffset=\dimexpr\voffset+.5in
\textheight=\dimexpr\textheight-.5in

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\cfoot{\sf \thepage}
\lfoot{\sf AP Strength and Fitness Test}
\rfoot{\tt \href{https://github.com/jedp/barbell-AP}{github.com/jedp/barbell-AP}}

\begin{document}

\smash{\Shortstack[l]{%
  \sffamily\Huge {\sf\bf AP} Strength and Fitness\\
%%  {\sffamily\Huge Bubble Answer Sheet}\\
  Name \underline{\hspace{2.4in}} Instructor\underline{\hspace{1.2in}}
    Date\underline{\hspace{1.2in}}\\
%%  \textcolor{black!50}{\rule{5.9in}{2ex}}\\
  \strut\\
  \sampleblock\\
  \rule{0ex}{4pt}\\}%
}\vspace{-\baselineskip}\par

\smallskip
\def\qCount{20}
\generateTable{\qCount}

\bigskip

{ }

\bigskip

{ }

\bigskip

{ }

\bigskip


\small

\begin{enumerate}

  \item Do you even lift?

  \begin{enumerate}[label=(\alph*)]
    \item Bruh?
    \item Bruh.
    \item Bruh \dots
    \item Bruh!
  \end{enumerate}

\item A healthy diet includes:

  \begin{enumerate}[label=(\alph*)]
    \item Little animal-based saturated fats
    \item Little-animal-based saturated fats
    \item Fat little animals sated with bass
    \item Animals lilting fatuously ``bases loaded''
  \end{enumerate}

\item Smoking is

  \begin{enumerate}[label=(\alph*)]
    \item Cool
    \item Bad
    \item Expensive
    \item All of the above
  \end{enumerate}


\item There are some individuals who might be eating a healthy diet, exercising
  regularly, and lifting weights, but still have \underline{\hspace{1in}}.


  \begin{enumerate}[label=(\alph*)]
    \item hygiene
    \item ennui
    \item osteoporosis
    \item the Sunday Scaries
  \end{enumerate}

\item Which is not an essential amino acid?

  \begin{enumerate}[label=(\alph*)]
    \item Methionine
    \item Leucine
    \item Tryptophan
    \item Isolde
  \end{enumerate}

\item Animal-based proteins have been shown to produce a rapid rise in
  postprandial blood EAA levels, which subsequently produces a large increase
  in muscle protein synthesis rates. Which is the best synonym for
  ``postprandial'' in this context?

  \begin{enumerate}[label=(\alph*)]
    \item occurring after the eating of shrimp
    \item exdeglutitive
    \item absolutely sabulous
    \item peresculentative
  \end{enumerate}

\item EMOM stands for

  \begin{enumerate}[label=(\alph*)]
    \item e-mom
    \item every minute on the minute
    \item Ethel Merman, only Merman
    \item English Mational Opera Morth (now Opera Morth)
  \end{enumerate}

\pagebreak

\item As you know, B\o{}rge Fagerli coined the term ``myo-rep'' sometime in the
  mid 2000s. What was he talking about?

  \begin{enumerate}[label=(\alph*)]
    \item Myosis Repugnandi (the ocular disgust reflex)
    \item One of any Alliance High Command intellitence reports regarding the
      infamous Abyssin scout, Myo, formerly of the Outer Rim territories
    \item Something about muscles and repetition
    \item The standard Metropolitan Youth Orchestra Repertoire
  \end{enumerate}


\item They say muscle hypertrophy follows a dose{}--{}response relationship, with
  increasingly greater gains achieved with higher training volumes.

  \begin{enumerate}[label=(\alph*)]
    \item They do, do they?
    \item No discomfort, no expansion.
    \item Those dietary confoundings of results, tho.
    \item Sorry, I wasn't listening?
  \end{enumerate}


\item From the following list, MWS and HWS, with respect to LWS, can best be described as

  \begin{enumerate}[label=(\alph*)]
    \item weatherbeaten
    \item clothed with authority
    \item stale ({\it of bread, etc}.)
    \item narcotizing ({\it fig}.)
  \end{enumerate}


\item Which of the following does not cause muscle growth?

  \begin{enumerate}[label=(\alph*)]
    \item Metabolic stress
    \item Mechanical tension
    \item Muscle damage
    \item Motivational interviewing
  \end{enumerate}


\item Pain in the chest often coincides with

  \begin{enumerate}[label=(\alph*)]
    \item Miosis
    \item Meiosis
    \item Myosis
    \item Mayo
  \end{enumerate}


\item Thigh bone connected to the

  \begin{enumerate}[label=(\alph*)]
    \item Knee bone
    \item Leg bone
    \item Hip bone
    \item Toe bone
  \end{enumerate}


\item The gastrocnemius is

  \begin{enumerate}[label=(\alph*)]
    \item A specialist in motion pictures concerning restaurants
    \item The ``tummy'' of your shin
    \item Gut feeling
    \item An anagram of ``goats or cis men''
  \end{enumerate}


\item In her well-known manual {\it Physiology and Calisthenics}, 1856,
  Catherine Beecher wrote: ``The most terrible evils and deformities
  that afflict humanity have arisen from the abuses of
  \underline{\hspace{1in}}.''

  \begin{enumerate}[label=(\alph*)]
    \item the Auto--Tune device
    \item dress
    \item the Catholic church before the Reformation
    \item statistics
  \end{enumerate}


\item In his {\it Manual of Musical Drill and System of Physical Training for
  the use of Teachers in Schools}, George Cruden, A.M., prescribes these
  dimensions for Indian clubs:

  \begin{itemize}
    \item For infants: 1 foot 8 inches by 3 inches
    \item For adults: 2 feet 4 inches by 4 inches
  \end{itemize} 

  What dimensions does he propose for use by boys and girls?

  \begin{enumerate}[label=(\alph*)]
    \item 1 foot 9 inches by 4 inches
    \item 1 foot 11 inches by 3 inches
    \item 1 foot 11 inches by 4 inches
    \item 2 feet by 4 inches
  \end{enumerate}

\pagebreak

\item The music to accompany the opening of ranks for the Indian Club
  Excercises in Cruden's {\it Manual} is a march in D major. This is
  interesting because the accompaniments for all the subsequent excercises are
  waltzes, exercises 1--10 of which are either in F major or B-flat major,
  while 11--18 were composed entirely in \underline{\hspace{1in}}.

  \begin{enumerate}[label=(\alph*)]
    \item E-flat major
    \item G major
    \item C minor (Dorian mode)
    \item Asia Minor
  \end{enumerate}


\item In his {\it Swedish System of Educational Gymnastics}, 1891, Baron Nils
  Posse reminds us that ``Medical gymnastics have been known in America under
  the name `Swedish Movements'.'' By contrast, a classic live recording by jazz
  pianist and vocalist Les McCann is called

  \begin{enumerate}[label=(\alph*)]
    \item Norwegian Movement
    \item Swiss Movement
    \item Swabian Movement
    \item St. Nemevomh Sidews
  \end{enumerate}


\item In 1930, Juan Carlos Ceriani, an instructor in Montevideo, Uruguay,
  created a game for recreation in the YMCA called

  \begin{enumerate}[label=(\alph*)]
    \item Sitfit
    \item Balena
    \item Albal
    \item Futsal
  \end{enumerate}


\item In the 1985 film {\it Perfect}, which chronicles the appeal aerobics
  classes held for single people in that benighted decade, Adam Lawrence
  (played by John Travolta) engages in protracted pelvic exercises with Jesse
  Wilson (Jamie Lee Curtis), as a result of which he loses his

  \begin{enumerate}[label=(\alph*)]
    \item journalistic objectivity
    \item academic skepticism
    \item cartesian dualism
    \item human dignity ({\it Menschenw\"urde})
  \end{enumerate}


\end{enumerate}

\end{document}
